Late Fusion via Subspace Search with Consistency Preservation

### 2017-07-28 aaai-2018/main.tex
add aaai-2018

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%%
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{epstopdf}
\usepackage{bm}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand\mycomment[1]{}

\def\ranksym{p}
\def\symp{r}

\def\calP{\mathcal{P}}
\def\M{\mathcal{M}}
\def\R{{\mathbb R}}
\def\bR{{\bf R}}
\def\U{{\bf U}}
\def\V{{\bf V}}
\def\diag{\mbox{diag}}
\def\bsigma{\mbox{{\boldmath $\sigma$}}}
\def\trsp{{\sf T}}
\def\I{{\bf I}}
\def\0{{\bf 0}}
\def\G{{\bf G}}
\def\grad{{\text{grad}}}
\def\bZ{{\bf Z}}
\def\bfeta{\mbox{{\boldmath $\eta$}}}
\def\mT{{\mathcal T}}

@@

\def\yanred{\textcolor{black}}
\def\yanblue{\textcolor{blue}}
\def\kuired{\textcolor{red}}
%%%%%

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{283} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Late Fusion via Subspace Search with Consistency Preservation}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

\begin{abstract}
In many real-world applications, data can be represented by multiple ways or multi-view features, in order to describe various characteristics of data. In this sense, the prediction performance can be significantly improved by taking advantages of these features together. Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance. However, it is ubiquitous that different features dispute the prediction on the same data with each other, leading to performance degeneration. In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources, aiming to avoid the performance degeneration caused by the controversy of multiple features. In this way, the consistency of results by various features can be preserved, which can relieve the performance degeneration. Extensive experiments demonstrate the efficacy of the proposed method for outlier detection and performance improvement, which outperforms the previous state-of-the-art late fusion algorithms on most datasets.
\end{abstract}

@@

%背景 多model融合
Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
There are often multiple ways to generate numerical features from raw data for visual recognition.
For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
(SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf)~\cite{manning2008introduction} and word2vec~\cite{mikoloviclr2013efficient}.
Each category of features tends to capture some specific characteristics of data,
such as textures of images and frequencies of text data.
When building a prediction model, the model trained on one kind of features could be biased and hence may incur unsatisfactory performance.
Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.

@@

To avoid the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
This is a hard constraint, and it is different from~\cite{gaoijcai2016robust,ye2012robust} which introduce a soft constraint on the low-rank property.
On the other hand, to remove the abnormal predictions generated by individual features, we propose to filter out these inconsistent results by using the $\ell_{1,2}$ regularization (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
\yanred{
Specially, $\ell_{1,2}$ loss preserves the fidelity within each column by $\ell_{2}$ loss in the vertical direction and is robust to sparse errors across all the columns by $\ell_{1}$ loss in the horizontal direction.
Compared to $\ell_{1,2}$ loss, $\ell_{2}$ loss is sensitive to outliers, so that may not produce robust and satisfactory predictions.
$\ell_{1}$ loss is not sensitive to outliers, but not capable to detect the abnormal features which generate corrupted results.
}
In addition, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
Thus, we in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

The main contributions of this work are summarized as follows:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem, which is the first attempt to introduce a hard constraint on the low-rank property to the late fusion problem.
      Our model intuitively removes inconsistent predictions made by abnormal features and preserves the consistency of predictions from different sources.
  \item We propose an ALM-based algorithm to enable matrix recovery algorithms to handle non-smooth $\ell_{1,2}$ loss, rather than a simple least square loss which has been frequently studied in literature.
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item We provide theoretical convergence analysis for the proposed robust matrix recovery algorithm.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,Mishra2012,ngonips2012scaled}.
For instance, in~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
%The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
In \cite{jain2013low} the authors propose a alternating minimization method for matrix factorization with a global optimality guarantee,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method cannot be guaranteed the global optimality in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method may converge faster than the alternating minimization approach.
However, most existing matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

Some other fusion algorithms are proposed for specific tasks.
The authors of \cite{zheng2015query} estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
Zha \etal \cite{zha2015exploiting} use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
The authors in~\cite{vanicassp2014late} point out that missing values in predictions can be a challenge for late fusion due to the absence of features.
These special designed fusion algorithms can be hard to extend to general problems, being lack of generalization.

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ ($1 \leq j \leq m$) on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
$
|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }  .
$
Thus, a general formulation of recovering the underlying low-rank label matrix can be written as follows:
{
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \calP_{\Omega} (\bL - \bX) ||_{1,2}~~~~~~\st~~\rank(\bX) = p
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
$\Omega$ denotes a subset containing the indices of the observed entries,
and $p$ is a scalar.
Here $\calP_{\Omega}$ denotes the orthogonal projection onto the linear space of matrices support on $\Omega: \calP_{\Omega}(\bX) = \bX_{ij}$ if $(ij) \in \Omega$; $\calP_{\Omega} = 0$ otherwise.
This includes some cases where missing elements may occur~\cite{vanicassp2014late}.
In our setting, to preserve the consistency among various classifiers, we set the hard constraint of the rank, \ie, $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as follows:
{
\begin{align}\label{eq:l12_mf}
  \min_{\bX} || \calP_{\Omega}(\bL - \bX) ||_{1,2} ,~  \st~ \rank(\bX) = p  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

By introducing a new variable $\calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)  ,~ \rank(\bX) = p  .
\end{align}
}
\noindent
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2
\end{align}
}
\noindent
where $\rank (\bX) = p$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.
The following lemma and theorem provide the theoretical convergence guarantee of the proposed algorithm.
We emphasize that our problem is a non-convex problem with a rank constraint, which is rarely studied in previous literatures.

@@

\begin{proof}
  The proof can be found in Appendix A.
  \mycomment{
  By the optimality of $\bE_{t+1}$ in Step 2 in Algorithm~\ref{alg:alm_mf}, we have the sub-differential of $\calL$ w.r.t. $\bE$ as zeros:
  {
  \begin{align}
  \label{eq:derivatives_calL_E}
    0 & \in \frac{\calL(\bX_{t+1}, \bE_{t}, \blambda_{t}, \mu_{t})}{\bE_{t+1}} \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t} + \mu_{t} (\calP_{\Omega} (\bL - \bX_{t+1} - \bE_{t+1})) \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t+1}   \nonumber \\
    \Rightarrow & -\blambda_{t+1} \in \partial(|| \bE_{t+1} ||_{1,2})  .
  \end{align}
  }
  \noindent
  Consider the computation of $\bE_{t+1}$ in Eq~(\ref{eq:column_wise_soft_thresholding}), which is associated with $\bL, \bX_{t+1}$, $\blambda_{t}$ and $\mu_{t}$.
  $\bL$ is the observation and thus bounded.
  $\bX_{t+1}$ is bounded due to the convergence guarantee of Step 1 in Algorithm~\ref{alg:alm_mf}~\cite{vandereycken2013lowrank}.
  $\{ \blambda_{t} \}$ is initialized by setting $\blambda_{0} = 0$ and $\{ \mu_{t} \}$ is non-decreasing.
  Thus when updating by Algorithm~\ref{alg:alm_mf}, $\bE_{t+1}$, $\partial(\bE_{t+1})$ and $\blambda_{t}$ are all bounded accordingly as $t$ increases.
  This completes the proof.
  }
\end{proof}

@@

\subsection{Subproblem Optimization w.r.t. $\bX$}

To update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2  \nonumber  \\
              = & \frac{\mu}{2} || \calP_{\Omega} (\bM - \bX) ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} || \calP_{\Omega} (\bM - \bX) ||_F^2,~ \st~ \rank(\bX) = p.
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.

>>>>

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required

%%%%%
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{epstopdf}
\usepackage{bm}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newcommand\mycomment[1]{}

\def\ranksym{p}
\def\symp{r}
\def\calP{\mathcal{P}}
\def\M{\mathcal{M}}
\def\R{{\mathbb R}}
\def\bR{{\bf R}}
\def\U{{\bf U}}
\def\V{{\bf V}}
\def\diag{\mbox{diag}}
\def\bsigma{\mbox{{\boldmath $\sigma$}}}
\def\trsp{{\sf T}}
\def\I{{\bf I}}
\def\0{{\bf 0}}
\def\G{{\bf G}}
\def\grad{{\text{grad}}}
\def\bZ{{\bf Z}}
\def\bfeta{\mbox{{\boldmath $\eta$}}}
\def\mT{{\mathcal T}}

@@

\def\eg{\emph{e.g}.} \def\Eg{\emph{E.g}.}
\def\ie{\emph{i.e}.} \def\Ie{\emph{I.e}.}
\def\cf{\emph{c.f}.} \def\Cf{\emph{C.f}.}
\def\etc{\emph{etc}.} \def\vs{\emph{vs}.}
\def\wrt{w.r.t.} \def\dof{d.o.f.}
\def\etal{\emph{et al}.}
%%%%%

%PDF Info Is Required:
\pdfinfo{
/Title (Late Fusion via Subspace Search with Consistency Preservation)
/Author (AAAI Press Staff)
}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Late Fusion via Subspace Search with Consistency Preservation}
\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}
\maketitle
\begin{abstract}
In many real-world applications, data can be represented by multiple ways or multi-view features, in order to describe various characteristics of data. In this sense, the prediction performance can be significantly improved by taking advantages of these features together. Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance. However, it is ubiquitous that different features dispute the prediction on the same data with each other, leading to performance degeneration. In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources, aiming to avoid the performance degeneration caused by the controversy of multiple features. In this way, the consistency of results by various features can be preserved, which can relieve the performance degeneration. Extensive experiments demonstrate the efficacy of the proposed method for outlier detection and performance improvement, which outperforms the previous state-of-the-art late fusion algorithms on most datasets.
\end{abstract}

@@

%背景 多model融合
Feature representation of objects, which transforms raw data into numerical features, is a prerequisite for most real-world applications.
There are often multiple ways to generate numerical features from raw data for visual recognition.
For example, for image data, one can construct hand-crafted features such as scale-invariant feature transform
(SIFT) feature~\cite{loweijcv2004distinctive} and Histograms of Gradients (HOG) feature~\cite{dalalcvpr2005histograms},
or extract features based on well-trained convolutional neural networks (CNNs)~\cite{krizhevsky2012imagenet}.
Moreover, text data can be represented by term frequency–inverse document frequency (tf-idf) and word2vec.
Each category of features tends to capture some specific characteristics of data,
such as textures of images and frequencies of text data.
When building a prediction model, the model trained on one kind of features could be biased and hence may incur unsatisfactory performance.
Existing works have investigated the performance improvement by combining multiple kinds of features in real-world applications~\cite{gehler2009feature,ye2012robust,xuiccv2013feature,lai2015learning}.

@@

To avoid the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
This is a hard constraint, and it is different from~\cite{gaoijcai2016robust,ye2012robust} which introduce a soft constraint on the low-rank property.
On the other hand, to remove the abnormal predictions generated by individual features, we propose to filter out these inconsistent results by using the $\ell_{1,2}$ regularization (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
Specially, $\ell_{1,2}$ loss preserves the fidelity within each column by $\ell_{2}$ loss in the vertical direction and is robust to sparse errors across all the columns by $\ell_{1}$ loss in the horizontal direction.
Compared to $\ell_{1,2}$ loss, $\ell_{2}$ loss is sensitive to outliers, so that may not produce robust and satisfactory predictions.
$\ell_{1}$ loss is not sensitive to outliers, but not capable to detect the abnormal features which generate corrupted results.
In addition, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
Thus, we in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

The main contributions are summarized as follows:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem, which is the first attempt to introduce a hard constraint on the low-rank property to the late fusion problem.
      Our model intuitively removes inconsistent predictions made by abnormal features and preserves the consistency of predictions from different sources.
  \item We propose an ALM-based algorithm to enable matrix recovery algorithms to handle non-smooth $\ell_{1,2}$ loss, rather than a simple least square loss which has been frequently studied in literature.
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item We provide theoretical convergence analysis for the proposed robust matrix recovery algorithm.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion andalgorithms and feature fusion methods.
\end{itemize}

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,ngonips2012scaled}.
For instance, in~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
%In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
%The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
In \cite{jain2013low} the authors propose a alternating minimization method for matrix factorization with a global optimality guarantee,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method cannot be guaranteed the global optimality in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method may converge faster than the alternating minimization approach.
However, most existing matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

Some other fusion algorithms are proposed for specific tasks.
The authors of \cite{zheng2015query} estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
Zha \etal \cite{zha2015exploiting} use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
The authors in~\cite{vanicassp2014late} point out that missing values in predictions can be a challenge for late fusion due to the absence of features.
These special designed fusion algorithms can be hard to extend to general problems, being lack of generalization.

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ ($1 \leq j \leq m$) on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
{\small
\begin{align}
|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
\end{align}
}\noindent
Thus, a general formulation of recovering the underlying low-rank label matrix can be written as follows:
{\small
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \calP_{\Omega} (\bL - \bX) ||_{1,2}~~~~~~\st~~\rank(\bX) = p
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
$\Omega$ denotes a subset containing the indices of the observed entries,
and $p$ is a scalar.
Here $\calP_{\Omega}$ denotes the orthogonal projection onto the linear space of matrices support on $\Omega: \calP_{\Omega}(\bX) = \bX_{ij}$ if $(ij) \in \Omega$; $\calP_{\Omega} = 0$ otherwise.
This includes some cases where missing elements may occur~\cite{vanicassp2014late}.
In our setting, to preserve the consistency among various classifiers, we set the hard constraint of the rank, \ie, $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as follows:
{\small
\begin{align}\label{eq:l12_mf}
  \min_{\bX} || \calP_{\Omega}(\bL - \bX) ||_{1,2} ,~  \st~ \rank(\bX) = p  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

By introducing a new variable $\calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{\small
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)  ,~ \rank(\bX) = p  .
\end{align}
}
\noindent
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{\small
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2
\end{align}
}
\noindent
where $\rank (\bX) = p$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.
The following lemma and theorem provide the theoretical convergence guarantee of the proposed algorithm.
We emphasize that our problem is a non-convex problem with a rank constraint, which is rarely studied in previous literatures.

@@

\begin{proof}
  The proof can be found in Appendix A.
  \mycomment{
  By the optimality of $\bE_{t+1}$ in Step 2 in Algorithm~\ref{alg:alm_mf}, we have the sub-differential of $\calL$ w.r.t. $\bE$ as zeros:
  {\small
  \begin{align}
  \label{eq:derivatives_calL_E}
    0 & \in \frac{\calL(\bX_{t+1}, \bE_{t}, \blambda_{t}, \mu_{t})}{\bE_{t+1}} \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t} + \mu_{t} (\calP_{\Omega} (\bL - \bX_{t+1} - \bE_{t+1})) \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t+1}   \nonumber \\
    \Rightarrow & -\blambda_{t+1} \in \partial(|| \bE_{t+1} ||_{1,2})  .
  \end{align}
  }
  \noindent
  Consider the computation of $\bE_{t+1}$ in Eq~(\ref{eq:column_wise_soft_thresholding}), which is associated with $\bL, \bX_{t+1}$, $\blambda_{t}$ and $\mu_{t}$.
  $\bL$ is the observation and thus bounded.
  $\bX_{t+1}$ is bounded due to the convergence guarantee of Step 1 in Algorithm~\ref{alg:alm_mf}~\cite{vandereycken2013lowrank}.
  $\{ \blambda_{t} \}$ is initialized by setting $\blambda_{0} = 0$ and $\{ \mu_{t} \}$ is non-decreasing.
  Thus when updating by Algorithm~\ref{alg:alm_mf}, $\bE_{t+1}$, $\partial(\bE_{t+1})$ and $\blambda_{t}$ are all bounded accordingly as $t$ increases.
  This completes the proof.
  }
\end{proof}

@@

\subsection{Subproblem Optimization w.r.t. $\bX$}
\label{sec:sub_x}

To update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{\small
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2  \nonumber  \\
              = & \frac{\mu}{2} || \calP_{\Omega} (\bM - \bX) ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{\small
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} || \calP_{\Omega} (\bM - \bX) ||_F^2,~ \st~ \rank(\bX) = p.
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.
